%----------------------------------------------------------------------------
\chapter*{Introduction}\addcontentsline{toc}{chapter}{Introduction}
%----------------------------------------------------------------------------
\section{Natural Language Processing}
While computers can be easily programmed to understand structured data, such as tables and spreadsheets, it can be rather challenging for them
to understand human communication. Because there is a vast difference in the magnitude of the unstructured data compared to the structured ones, there is a high demand
for tools, that can deal with raw text. Thats where NLP comes in. It contains high variety of tools, that we have to use, when we need to deal with natural input.

Every day, we come into contact with human communication, we say a lot of words to other people, and they try to interpret them even when the context of the saying 
isn't necesseraily complete. The listeners can use their common knowledge to fill the needed information. We resolve ambiguities, misunderstanding, and can even understand words 
we have never heard before just from the context of the communication.
Even though these tasks are trivial for us, for a computer it can be really hard.

%--------------------------------------------------------------------------------------
% egyszerü multtol jelenig bevezeto
The interest in NLP research began in the 1950s, the early phase was mainly focused on ML (Machine Translation), because after the World War II, people
recognised the importance of the translation from one language to another, and hoped to do it automatically.
However ML is still a very difficult nowadays, so these researches discovered early the main challenges of the syntactic and semantic parsing.
As time passed, researches embraced new areas of NLP as more advanced technology and knowledge became available. Now that we live in a world where
computers and smartphones, collecting data became incredibly easy, as a result, statistical NLP drew attention because these models thrives off big data neural, but one cannot ignore 
simple rule based methods, which can also be very powerful method, especially using them as a hybrid model with statistical methods.
%--------------------------------------------------------------------------------------
% rövid nlp pipeline

%--------------------------------------------------------------------------------------
% semantic parsing bevezeto + modszerek + alkalmazasok jelenleg